Relationships in the extremes and their influence on competition and coexistence: Supporting information

### 2022-01-26 paper/SupMat.Rnw
writing about E and C choices

%***DAN: Jasmin, please start on this section when you get a chance. Here are some topics that need
%to be covered:
Estimations of $Q_i(t)$, $V_i(t)$, and $K_i(t)$, temperature dependence functions for cell quota, reproduction rate, and half saturation, respectively, were used to paramaterize the competing diatom model outline in the paper. 
Values of and subsequent function estimations are plotted in Figure \ref{fig:VQK}. 
Descamps and Julien obtained estimated values for $Q_i$, $V_i$, and $K_i$ from single species nine-day batch experiments at four different temperatures (6, 12, 18, 24) (see Table 1 of Descamps and Julien) and further computed a linear interpolation to define temperature dependence functions of $Q_i(t)$, $V_i(t)$, and $K_i(t)$. These values and functions are indicated in Figure \ref{fig:VKQ} by open circles and dashed lines. Ellner 2016 and 2019 chose to slightly modify some values and functions, indicated in Figure \ref{fig:VKQ} by closed circles and solid lines.

%1) Precise delineation of the functions Q_i, V_i, K_i which were used. There are different options considered
%all over the place in the code and by Ellner et al (2019) and by the original diatom study, so we have to
%be very clear here. To give one example of the need for care, here, Ellner et al (2019) state on p. 6
%of their paper that K_1 and K_2 were constant for the range of temperature considered, and they state
%that they took constant values for these things. However, we used a larger range of temperatures. 
%Depending on which of K1fun/K2fun versus K1flatfun/K2flatfun (from DDataAndVKQfuns.R) was actually used
%may make a difference, so we have to specify. Note that even K1flatfun/K2flatfun were not actually flat
%for the whole temperature range 6-24 degrees C, though they were for the range of temperature Ellner
%et al considered. We should not say we used flat K1 and K2 functions unless we are sure we only ever
%used temperatures in the flat ranges of these functions. Better just to describe the functions we
%actually used, where the best way to describe them *may* be by plotting them. Anyway, what you need to
%do is make sure you know what versions of each of these 6 functions your code actually used, and then
%describe the functions precisely in this section.

@@

>>>>

%***DAN: Jasmin, please start on this section when you get a chance. Here are some topics that need
%to be covered:
Estimations of $Q_i(t)$, $V_i(t)$, and $K_i(t)$, temperature dependence functions for 
cell quota, reproduction rate, and half saturation, respectively, were used to 
paramaterize the competing diatom model outline in the paper. 
Values of and subsequent function estimations are plotted in Figure \ref{fig:VQK}. 
\cite{Descamps_2005} obtained estimated values for $Q_i$, $V_i$, and $K_i$ from 
single species nine-day batch experiments at four different temperatures ($6^\circ$C, 
$12^\circ$C, $18^\circ$C, $24^\circ$C) (see Table 1 of \cite{Descamps_2005}) and further
computed a linear interpolation to define temperature dependence 
functions of $Q_i(t)$, $V_i(t)$, and $K_i(t)$. These values and functions are 
indicated in Figure \ref{fig:VKQ} by open circles and dashed lines. 
\cite{Ellne_2016, Ellner_2019} chose to slightly modify some values and functions 
(to better align model with competition experiments), 
%why did they make K_i's constant and do we need to adjust so that it
%is constant over the range of temperatures considered 
indicated in Figure \ref{fig:VKQ} by closed circles and solid lines. 
These modifications do not result in meaningful differences when evaluating 
coexistence at the parameter values used by \cite{Descamps_2005}.
We chose to implement the modified functiones in our methods to quantify and 
decompose coexistence.

%be very clear here. To give one example of the need for care, here, Ellner et al (2019) state on p. 6
%of their paper that K_1 and K_2 were constant for the range of temperature considered, and they state
%that they took constant values for these things. However, we used a larger range of temperatures. 
%Depending on which of K1fun/K2fun versus K1flatfun/K2flatfun (from DDataAndVKQfuns.R) was actually used
%may make a difference, so we have to specify. Note that even K1flatfun/K2flatfun were not actually flat
%for the whole temperature range 6-24 degrees C, though they were for the range of temperature Ellner
%et al considered. We should not say we used flat K1 and K2 functions unless we are sure we only ever
%used temperatures in the flat ranges of these functions. Better just to describe the functions we
%actually used, where the best way to describe them *may* be by plotting them. Anyway, what you need to
%do is make sure you know what versions of each of these 6 functions your code actually used, and then
%describe the functions precisely in this section.

@@

Our decomposition is defined by $E(t)=\theta(t)$, 
$C_j(t)=(K_j(t)+S(t))/S(t)$ and $r_j(E_j,C_j)=\frac{V_j(E)}{C_j} -D$. 
We note that our definition and selection of our "features" of interest are
options among many and features need not be limited to $E$ and $C$ \citep{Ellner_2019}. 
For example \cite{Ellner_2019} decomposes coexistence with respect to fluctuation in
inflow silicate concentration, $S$, and temperature, and \cite{Ellner_2016} decomposes
coexistence using classical $E$ and $C$ drivers, but define $E=V(t)$. 
Choice of drivers and their definitions are up to the investigator,
but should real variables that influence population growth.
Thus in our exploration, environmental fluctuation is temperature fluctuation.
